% Selfology Book 2: Путь в глубину
% Кластеры организованы по уровню глубины
% Сгенерировано: 2025-12-03 21:05
% Язык: en

\documentclass[11pt,a4paper,oneside]{book}
\usepackage{selfology-book}
\setdefaultlanguage{english}

\begin{document}

\bookcover{The Path Within}{From surface to truth}{2025}
\booktoc

\thispagestyle{empty}
\vspace*{0.2\textheight}

{\centering\sffamily\bfseries\fontsize{24pt}{28pt}\selectfont The Beginning\par}

\vspace{2em}

This book is designed as a descent.

You'll start at the surface---where it's safe and clear. Gradually, you'll go deeper. By the end, you'll reach places few people ever visit.

\vspace{1.5em}
{\sffamily\bfseries Three Depths}

\textbf{Part I: First Steps.} Warm-up. Simple questions to help you tune into honest conversation with yourself.

\textbf{Part II: Exploration.} The work begins here. Questions will touch on things you haven't thought about. That's normal.

\textbf{Part III: Deep Work.} The most important part. Only go here when you're ready. Don't rush.

\vspace{1.5em}
{\sffamily\bfseries Why This Way}

We're made of layers. On top---what we know about ourselves and share easily. Deeper---what we know but don't like to admit. Even deeper---what we hide from ourselves.

Jumping straight to the depths hurts and doesn't help. You need a gradual descent. This book is your guide.

\newpage
\thispagestyle{empty}
\vspace*{0.1\textheight}

{\sffamily\bfseries How to Proceed}

\textbf{Sequentially.} Don't skip ahead. Each part prepares you for the next.

\textbf{With pauses.} Take breaks between parts---a day, a week. Let it settle.

\textbf{In writing.} A thought written by hand becomes more real. Don't answer in your head.

\textbf{Honestly.} No one will check this book. Lying here means lying only to yourself.

\vspace{2em}
{\centering\itshape Let's start simple.\par}

\part{Part I: First Steps}
\partsubtitle{Gentle start --- getting to know yourself}
\programbreak

\clusterWithProgram{Here and~Now}{5–10 min}{where I~am now}{Think About Life}

\questionF{1. Describe your current state in~three words?}

\questionF{2. What does your typical morning look like?}

\questionF{3. What do you do when you have free time and~no one expects anything from you?}

\questionF{4. When was the~last time you felt completely energized and~full of~vitality? What was happening around you?}


\clusterWithProgram{Where I~am now}{5–10 min}{my~work affairs}{Think About Career or~Business}

\questionF{1. In~which field are you currently working or~studying?}

\questionF{2. How long have you been in~this field?}

\questionF{3. Do you have relevant education in~your current field?}

\questionF{4. Do you work in~the~office, remotely, or~through a~hybrid model?}

\questionF{5. What is your current work schedule like?}


\clusterWithProgram{Sleep and~Recovery}{5–10 min}{my~sleep and~rest}{Think About Health}

\questionF{1. What time do you usually go to~bed, and~what time do you wake up?}

\questionF{2. How many hours do you typically sleep each night?}

\questionF{3. How do you usually feel in~the~mornings: energetic, sluggish, or~drowsy?}

\questionF{4. What do you usually do in~the~hour before bed? Does it~help you fall asleep?}

\questionF{5. Are you more of~an~early bird or~a~night owl, and~what does this bring to~your life?}


\clusterWithProgram{Archetypes and~Models}{5–10 min}{who influenced me}{Know Yourself}

\questionF{1. Who has had the~strongest influence on~you, and~what qualities or~approaches of~theirs do you find in~yourself?}

\questionF{2. Whom do you admire most, and~why this person specifically?}


\clusterWithProgram{Emotion Map}{5–10 min}{do I~like my~work?}{Improve Emotional State}

\questionF{1. Which emotions do you notice most often throughout your day?}

\questionF{2. Identify one emotion that surprises you with how frequently it~appears.}

\questionF{3. Is there an~emotion that constantly resides in~your body, like background noise?}


\clusterWithProgram{Goal Inventory}{5–10 min}{my~goals for~today}{Reviewing Goals}

\questionF{1. List all the~goals you are currently pursuing (professional, personal, financial).}

\questionF{2. Where did each of~these goals come from: your own choices or~other people's expectations?}

\questionF{3. Which goal is it~time to~let go of---one that no longer serves or~inspires you?}

\questionF{4. Perhaps the~goals weighing you down are no longer relevant to~your life?}


\clusterWithProgram{What is a~dream for~me}{5–10 min}{what does it~mean to~dream}{Dreamers}

\questionF{1. Think back to~your childhood: what did you dream about then? What has changed since?}

\questionF{2. What is your main dream right now?}

\questionF{3. Is this truly your dream, or~is it~something you once heard from others and~adopted as~your own?}

\questionF{4. To~what extent are you living your dream life right now?}


\clusterWithProgram{What I~Learned About Myself}{5–10 min}{What I~understood about myself}{Reflection}

\questionF{1. What self-discovery turned out to~be the~most unexpected?}

\questionF{2. What did you discover about yourself that you didn't know before reflecting on~this?}

\questionF{3. What beliefs about yourself have you recently reconsidered or~changed?}


\clusterWithProgram{Acceptance}{5–10 min}{what I~am ready to~accept}{3 Pillars of~Purification}

\questionF{1. Which part of~yourself did you once reject but~were able to~accept over time?}

\questionF{2. How did your life change when you accepted what you used to~fight against?}

\questionF{3. Which part of~you is still waiting to~be accepted?}


\clusterWithProgram{People as~a~Resource}{5–10 min}{who supports me}{Resource}

\questionF{1. Who has had a~particularly strong influence on~you, and~what exactly did this person do or~say?}

\questionF{2. Who would you say your main source of~support is right now?}

\questionF{3. Whom can you rely on~during tough times, and~why specifically these people?}

\questionF{4. Who believes in~you, even when you doubt yourself?}


\clusterWithProgram{What is a~boundary for~me}{5–10 min}{what it~means to~dream}{Personal Boundaries}

\questionF{1. Where do you often let people cross your boundaries?}

\questionF{2. Why do you allow this---out of~fear, politeness, or~habit?}

\questionF{3. With whom do you find it~easier to~set boundaries, and~with whom is it~more difficult? Why?}


\clusterWithProgram{Getting to~Know Fear}{5–10 min}{Do I~like my~work?}{Working with Fears}

\questionF{1. What fear has lived inside you for~so~long that it's become part of~who you are?}

\questionF{2. How often does this fear arise? When is it~triggered?}

\questionF{3. Where in~your body do you feel fear?}

\questionF{4. Which potential future scenario causes you the~most anxiety or~worry?}


\clusterWithProgram{Map of~My Relationships}{5–10 min}{my~close and~distant ones}{Understanding Relationships}

\questionF{1. How many people truly know the~real you? Who are they?}

\questionF{2. Who in~your life makes you feel safe being yourself?}

\questionF{3. Who exemplifies harmonious and~healthy relationships for~you?}

\questionF{4. How satisfied are you with your friendships right now? Rate them on~a~scale from 1 to~10.}


\clusterWithProgram{Signs of~Burnout}{5–10 min}{what I~feel and~notice}{Burnout  Resource}

\questionF{1. What happens to~your body when you're exhausted? What signals is your body sending?}

\questionF{2. What emotion is hiding behind your chronic fatigue?}

\questionF{3. When do you feel anger but~label it~as~tiredness or~irritation?}

\questionF{4. When do your goals energize you, and~when do they begin to~drain you?}


\clusterWithProgram{Acknowledging What Was}{5–10 min}{My~truth about the~past}{Healing the~Past}

\questionF{1. What event from your past still resonates with you today?}

\questionF{2. What lesson did you learn from the~most challenging period of~your life?}

\questionF{3. What important thing have you learned recently?}

\questionF{4. How have you become stronger recently, and~what has this provided you?}


\clusterWithProgram{Body Sensations Map}{5–10 min}{what my~body is telling me}{Body and~Emotions}

\questionF{1. Where in~your body do you feel joy? Describe the~sensation: warmth, lightness, and~expansion.}

\questionF{2. Consider a~moment when you felt overwhelmed with gratitude. What did you feel in~your body during that time?}

\questionF{3. Think of~an~emotion that brings you peace. How does it~feel in~your body?}

\questionF{4. Where in~your body do you feel the~deepest emotion that you can't express in~words?}


\clusterWithProgram{Origin of~Beliefs}{5–10 min}{who influenced me}{Money and~Self-Worth}

\questionF{1. What financial lessons did you learn from your parents? Both the~beneficial and~the~less helpful ones---everything matters for~understanding.}

\questionF{2. What beliefs about money did you learn from your family and~social environment, and~how do they influence your life now?}

\questionF{3. How did your parents approach money, and~what aspects of~their attitude do you notice in~yourself now?}


\clusterWithProgram{Current Beliefs}{5–10 min}{my~rules about money}{Money and~Self-Worth}

\questionF{1. What beliefs about money are living within you right now?}

\questionF{2. What beliefs do you currently hold about money, and~how are they affecting your financial situation?}

\questionF{3. How do you relate to~money---do you see it~more as~an~opportunity or~a~limitation?}

\questionF{4. How do you handle money when you're stressed? What might this reveal about your beliefs?}


\clusterWithProgram{Current Status}{5–10 min}{my~money today}{Money and~Self-Worth}

\questionF{1. How would you describe your current financial situation?}

\questionF{2. Where exactly are you investing your money right now -- in~your future (education, assets, investments) or~in~the~present (comfort, entertainment, status purchases)?}

\questionF{3. What portion of~your income do you allocate to~personal development?}


\clusterWithProgram{Expectations vs Reality}{5–10 min}{my~truth about the~past}{Crisis 27 / 45}

\questionF{1. When you were young, who did you imagine you would become at~this age?}

\questionF{2. Who are you, really, at~this moment? Does this align with your expectations?}

\questionF{3. What happened differently from what you planned?}

\questionF{4. What are you grateful for~in~your life not going according to~plan?}


\clusterWithProgram{Current Crisis}{5–10 min}{what doesn't satisfy me}{Crisis 27 / 45}

\questionF{1. What in~your life is currently causing a~crisis or~a~feeling of~being stuck?}

\questionF{2. Have you lost the~meaning in~what used to~energize you?}

\questionF{3. What changes in~life are you currently dealing with in~relationships, work, your view of~yourself, or~future plans?}


\clusterWithProgram{My~Value}{5–10 min}{what I~can do}{AI Anxiety and~the~Future of~Work}

\questionF{1. What professional skills make you valuable and~essential in~your current job?}

\questionF{2. Which aspects of~your work can't be replaced by~a~machine or~AI?}

\questionF{3. Is emotional intelligence your primary professional asset? Why?}

\questionF{4. What do you do beyond your job description that your colleagues appreciate?}


\clusterWithProgram{Consumption Awareness}{5–10 min}{where does my~time go}{Info-obesity}

\questionF{1. How much time do you spend each day on~digital platforms such as~social media, news, and~messaging apps?}

\questionF{2. Which three apps do you open first in~the~morning?}

\questionF{3. When was the~last time you spent a~day without notifications, either by~turning them off completely or~switching to~"Do Not Disturb" mode?}

\questionF{4. Do you open apps with a~conscious purpose or~just out of~habit?}


\clusterWithProgram{Where I~Lose My~Power}{5–10 min}{what drains my~energy}{Learned Helplessness 2.0}

\questionF{1. What often paralyzes you in~moments when you need to~take action?}

\questionF{2. Where does your actual circle of~influence end, and~what lies beyond your control?}

\questionF{3. In~what situations do you tend to~feel powerless or~helpless?}

\questionF{4. What happens to~your body when you feel powerless? What signals does it~send you?}


\clusterWithProgram{Mapping My~World}{5–10 min}{my~real relationships}{Parasocial Dependency}

\questionF{1. How many people in~your life truly know the~real you, without any masks or~pretenses?}

\questionF{2. How many hours per week do you spend with real people in~person? Is that enough for~you?}

\questionF{3. Which people you know only online would you most like to~meet in~real life?}

\questionF{4. What kind of~content helps you feel less lonely?}


\clusterWithProgram{Space Transformation}{5–10 min}{my~world before and~after}{Hybrid Life --- Remote Work}

\questionF{1. How has your relationship with home changed since transitioning to~hybrid work?}

\questionF{2. What has remote work brought into your life?}

\questionF{3. What did you lose when your office became your bedroom?}

\questionF{4. How have your personal space and~energy changed after the~complete digital shift?}


\clusterWithProgram{Mapping of~Masks}{5–10 min}{my~different faces}{Authenticity vs Algorithms}

\questionF{1. What different versions of~yourself do you present in~various contexts---social media, work, family, or~among friends?}

\questionF{2. Which platforms do you use? Are you the~same person on~all of~them?}

\questionF{3. How many times a~day do you edit, filter, or~hide your image?}

\questionF{4. How would your life change if~you stopped trying to~adjust your image to~meet other people's expectations?}


\clusterWithProgram{My~Consumption}{5–10 min}{my~purchases and~habits}{Eco-guilt and~Climate Anxiety}

\questionF{1. What goods and~services do you consume daily? Do you ever think about where they come from?}

\questionF{2. What consumer habits did you inherit from your parents?}

\questionF{3. What eco-friendly habits do you already have? What would you like to~add or~change about your consumption?}

\questionF{4. What is the~environmental cost of~your typical day?}


\clusterWithProgram{Symptoms and~triggers}{5–10 min}{when doubt overwhelms you}{Impostor Syndrome in~the~LinkedIn Era}

\questionF{1. In~which moments do you feel you're not competent enough for~your role?}

\questionF{2. How does reading your colleagues' success posts on~social media affect your self-esteem?}

\questionF{3. Are you worried that one day someone will tap you on~the~shoulder and~say, "You don't belong here; leave"?}


\clusterWithProgram{Grounding}{5–10 min}{what my~body feels}{Sunday Anxiety}

\questionF{1. How would you describe your current state in~three words? For~example, tiredness, worry, anticipation.}

\questionF{2. When does rest stop being rest? Have you ever noticed that moment when relaxation shifts into an~inner anticipation of~Monday?}

\questionF{3. How do you feel about how you spent this weekend?}

\questionF{4. If~tomorrow weren't Monday, how would you spend this evening?}


\clusterWithProgram{Honest Diagnosis}{5–10 min}{what is really happening}{Parental Guilt Over Screen Time}

\questionF{1. How many hours a~day does your child spend in~front of~a~screen, and~how many of~those hours are so~you can take a~break?}

\questionF{2. Are you familiar with the~storyline of~your child's favorite game or~cartoon?}

\questionF{3. How much time do you spend on~your phone when your child is in~the~same room?}


\clusterWithProgram{Digital Pulse}{5–10 min}{where am I~with crypto}{Cryptocurrency FOMO}

\questionF{1. How often do you check your portfolio or~charts? Be honest: once a~day, every hour, or~with every notification?}

\questionF{2. Does the~market's performance affect your mood? When the~market is down, how does that impact your interactions with family and~loved ones?}

\questionF{3. Do you sleep with your phone, fearing you'll miss price movements overnight?}


\newpage

\part{Part II: Exploration}
\partsubtitle{Diving in --- exploring patterns}
\programbreak

\clusterWithProgram{People Around Me}{10–20 min}{who influences me}{Think About Life}

\questionE{1. Who has had a~particularly strong influence on~you? What exactly did this person do or~provide for~you?}

\questionE{2. With whom have you been spending the~most time lately?}

\questionE{3. Do these people help you grow and~develop, or~do they hold you back and~keep you stuck where you are?}

\questionE{4. What do you never discuss with your family?}

\questionE{5. What makes you feel unique compared to~your family?}


\clusterWithProgram{Dreams and~Ambitions}{10–20 min}{where I~want to~arrive}{Think About Life}

\questionE{1. How do you envision your ideal day off? Where do you spend your time, what do you do, and~whom do you spend it~with?}

\questionE{2. What do you dream of~when you imagine financial freedom?}

\questionE{3. What would you like to~learn first?}

\questionE{4. Why do you want to~go there specifically?}

\questionE{5. What would motivate you to~wake up at~the~crack of~dawn?}

\questionE{6. Imagine you've made the~world a~better place. What specifically has changed?}


\clusterWithProgram{Values and~Beliefs}{10–20 min}{what is important to~me}{Think About Life}

\questionE{1. What values have you set for~yourself? Write down at~least three.}

\questionE{2. What makes you unique compared to~your family and~close friends?}

\questionE{3. Complete this sentence: "If people knew that I~really..., they would...}

\questionE{4. Do you love yourself?}

\questionE{5. What is your relationship with yourself like? Do you treat yourself with warmth or~criticism? What influences this relationship?}


\clusterWithProgram{Defense and~Self-Deception}{10–20 min}{what I'm hiding from}{Think About Life}

\questionE{1. From what are you trying to~protect yourself when you deceive yourself?}

\questionE{2. What must you free yourself from before your next breakthrough?}

\questionE{3. What deep fears do you face in~your life?}

\questionE{4. What scares you the~most about being close to~other people?}


\clusterWithProgram{The~Past}{10–20 min}{my~journey until today}{Think About Life}

\questionE{1. Who were you a~year ago? Who are you now? How have you changed?}

\questionE{2. How would you rate your past year across the~main areas of~life on~a~scale from 1 to~10? What significant events in~each area influenced your rating?}

\questionE{3. Identify three habits that benefited you this year. How did they support you?}

\questionE{4. Think of~2-3 times when things didn't go as~expected. What good ultimately came from those situations in~your life?}

\questionE{5. What were you unable to~achieve this year, and~why? What are your thoughts about it~now?}

\questionE{6. Are you still angry at~yourself for~something or~unable to~forgive yourself for~it?}


\clusterWithProgram{Satisfaction}{10–20 min}{do I~like my~job?}{Think About Career or~Business}

\questionE{1. On~a~scale of~1 to~10, how satisfied are you with your work right now?}

\questionE{2. How do you feel about your work? What resonates with you, and~what doesn't?}

\questionE{3. How well do your personal values align with the~corporate culture of~your organization?}

\questionE{4. Do you ever find yourself criticizing yourself for~taking time to~rest, even when you work hard?}


\clusterWithProgram{Goals and~Dreams}{10–20 min}{my~dreams about work}{Think About Career or~Business}

\questionE{1. What does your dream job look like?}

\questionE{2. What would you do for~work if~all jobs paid the~same?}

\questionE{3. What would you do if~money weren't a~limitation?}

\questionE{4. Imagine: In~five years, you run into an~old friend. What would you proudly tell them about your work?}

\questionE{5. If~you knew you would definitely succeed, what would you start doing right now?}


\clusterWithProgram{Barriers and~Resources}{10–20 min}{what hinders and~what helps}{Think About Career or~Business}

\questionE{1. What, specifically, about your current job is holding you back from reaching your professional goals?}

\questionE{2. If~you need a~mentor in~your work, who might that be, and~how can you find such a~person?}

\questionE{3. If~you decide to~stop working tomorrow, how long could you live on~your savings?}

\questionE{4. Where exactly does your money go right now: toward your future (investments, education, development) or~toward your present (purchases, entertainment, comfort)?}


\clusterWithProgram{Choices and~Actions}{10–20 min}{my~next steps}{Think About Career or~Business}

\questionE{1. If~you decided to~make a~change in~your career, where would you like to~work?}

\questionE{2. Imagine a~scale: on~one side, rejections from job interviews; on~the~other, working somewhere you're not valued. Which would be more important for~you to~avoid?}

\questionE{3. What gives you confidence that your idea will work? What data, experience, or~observations support your choice?}

\questionE{4. If~you had all the~resources you needed---time, money, and~connections---what would you want to~do, and~how would you spend your time?}


\clusterWithProgram{Physiology}{10–20 min}{what I~eat and~how I~move}{Think About Health}

\questionE{1. How do you discern what your body needs and~what it~doesn't?}

\questionE{2. How much water do you drink per day? Do you notice a~connection between the~amount of~water you drink and~how you feel?}

\questionE{3. What types of~physical activities bring you joy?}

\questionE{4. What is your relationship with your physical health? What does being healthy mean to~you?}


\clusterWithProgram{Body Signals}{10–20 min}{what my~body feels}{Think About Health}

\questionE{1. What happens to~your body when you're exhausted? What are the~first signals your body sends?}

\questionE{2. Where in~your body do you most often feel tension building up? What is your body trying to~tell you?}

\questionE{3. When was the~last time you listened to~your body and~followed its signals instead of~pushing through?}


\clusterWithProgram{Energy and~Resources}{10–20 min}{where I~get my~strength from}{Know Yourself}

\questionE{1. How would you describe your current energy state in~three words?}

\questionE{2. When was the~last time you felt completely alive and~full of~energy? What was happening in~your life at~that moment?}

\questionE{3. What are the~three actions or~situations that restore your energy the~fastest?}


\clusterWithProgram{Values through pride}{10–20 min}{what I~am proud of}{Know Yourself}

\questionE{1. What are you most proud of, and~why does this matter so~much to~you personally?}

\questionE{2. What qualities or~traits do you know better than anyone else about yourself but~rarely discuss?}


\clusterWithProgram{Desires and~Fears}{10–20 min}{what I~want and~fear}{Know Yourself}

\questionE{1. What do you most want right now?}

\questionE{2. What fear resides deep within your soul? What is it~trying to~protect?}


\clusterWithProgram{Embodiment of~Emotions}{10–20 min}{what my~body is telling me}{Improve Emotional State}

\questionE{1. Where do you feel joy in~your body? Describe the~sensation: is it~a~feeling of~warmth, lightness, or~expansion?}

\questionE{2. Think of~a~moment when you were overwhelmed with gratitude. What did you feel in~your body?}

\questionE{3. What emotions bring you peace and~harmony, and~how do they manifest in~your body?}

\questionE{4. Where in~your body does the~emotion you can't express in~words reside?}


\clusterWithProgram{Awareness of~Feelings}{10–20 min}{what I~am feeling right now}{Improve Emotional State}

\questionE{1. How well do you notice your feelings when they arise? Rate yourself from 1 to~10.}

\questionE{2. Do you allow yourself to~simply feel what's there, or~do you often think you're not supposed to~feel this?}

\questionE{3. Which emotions do you allow yourself to~feel only when you're completely alone?}

\questionE{4. When someone asks, "What are you feeling?" is your first impulse to~answer honestly or~to~say what they expect to~hear?}


\clusterWithProgram{Defenses and~Masks}{10–20 min}{my~masks and~shields}{Improve Emotional State}

\questionE{1. Do you use humor or~sarcasm to~express or~hide your feelings?}

\questionE{2. Are there emotions you display as~a~substitute for~your true feelings?}


\clusterWithProgram{Emotions as~Information}{10–20 min}{what my~feelings are whispering to~me}{Improve Emotional State}

\questionE{1. What are your regular feelings telling you?}

\questionE{2. If~your anxiety were a~wise teacher, what lessons would it~be imparting to~you?}

\questionE{3. Which emotion do you often label as~bad, despite it~actually trying to~help you?}


\clusterWithProgram{Goal Verification}{10–20 min}{which of~the~goals are alive}{Reviewing Goals}

\questionE{1. Choose one goal that's important to~you. What is your confidence based on~that this specific path will lead you to~the~result?}

\questionE{2. What specific data or~experience gives you confidence in~achieving this goal? What makes you believe it~is actually attainable?}

\questionE{3. Could there be a~more effective approach to~achieving the~same goal? What would help you determine this?}

\questionE{4. Do your goals inspire you, or~do they make you feel anxious instead?}


\clusterWithProgram{Professional Goals}{10–20 min}{what I~want from work}{Reviewing Goals}

\questionE{1. What is your dream job? Picture it~in~detail: where it~takes place, what it~involves, and~the~kind of~people you interact with.}

\questionE{2. Which aspects of~your current job are already helping you progress toward your career goals, and~what else can you do to~advance further?}

\questionE{3. What is it~specifically about your current job that prevents you from achieving your career goals?}

\questionE{4. How much does your current job help you move toward your professional goals?}


\clusterWithProgram{Prioritization}{10–20 min}{what matters most right now}{Reviewing Goals}

\questionE{1. If~you could achieve only three goals out of~all the~ones you have, which would they be?}

\questionE{2. How will you know you're moving toward your goals in~the~right direction?}


\clusterWithProgram{Reality Testing}{10–20 min}{what is realistically achievable}{Dreamers}

\questionE{1. Do you know someone who is already living a~similar lifestyle or~working in~a~field that interests you? What helped them achieve it?}

\questionE{2. Could your dream be based on~limited information? What would help you understand its reality more deeply?}

\questionE{3. If~you had all the~opportunities and~resources available, what would you do first?}


\clusterWithProgram{Dream House}{10–20 min}{what my~dream looks like}{Dreamers}

\questionE{1. If~all your problems were solved and~everything in~your life fell into place, where would you live, and~what would your dream home look like?}

\questionE{2. Imagine your dream home. What makes it~special? Describe 3 to~5 details that make it~uniquely yours.}

\questionE{3. What small, safe step can you take today to~move closer to~your dream home?}


\clusterWithProgram{Dream Job}{10–20 min}{where to~work with joy}{Dreamers}

\questionE{1. How do you envision your dream job? Describe it~as~specifically as~possible.}

\questionE{2. What would need to~change in~your life for~you to~pursue your dream job?}

\questionE{3. Who can help you get closer to~your dream job? What contacts, knowledge, or~resources do you need?}


\clusterWithProgram{Money and~Investments}{10–20 min}{where does my~money go}{Dreamers}

\questionE{1. Where exactly is your money going right now: into your future (investments, education, assets) or~into your present (comfort, entertainment, purchases)?}

\questionE{2. What percentage of~your income do you invest in~making your dreams come true?}

\questionE{3. If~you could allocate 10\% of~your income to~make your dream come true, what would you spend it~on?}


\clusterWithProgram{Freedom and~Changes}{10–20 min}{what has changed in~me}{Reflection}

\questionE{1. What freedom arises from a~new understanding of~yourself?}

\questionE{2. What do you now permit yourself to~do that you didn't before?}

\questionE{3. What are you willing to~give up? What in~your life no longer serves you?}


\clusterWithProgram{Action}{10–20 min}{what do I~do next}{Reflection}

\questionE{1. Based on~your new insights, what action are you ready to~take today?}

\questionE{2. With whom can you share your new self-discoveries? Who is willing to~support you on~this journey?}


\clusterWithProgram{Letting Go}{10–20 min}{what you are ready to~let go of}{3 Pillars of~Purification}

\questionE{1. What have you been able to~let go of~this year---beliefs, habits, or~relationships?}

\questionE{2. What happens to~you when you let something go? How does this change your inner state?}

\questionE{3. What are you holding onto right now, even though you know it's time to~let go?}


\clusterWithProgram{Internal Resources}{10–20 min}{what gives me~strength}{Resource}

\questionE{1. What are you most proud of, and~why is this important to~you?}

\questionE{2. What is your main strength, and~how do you use it?}

\questionE{3. What past experience helps you now, and~what did it~teach you?}

\questionE{4. What are the~three qualities you consider to~be your greatest strengths?}


\clusterWithProgram{Material Resources}{10–20 min}{what I~have}{Resource}

\questionE{1. What material resources do you have available: money, assets, education, connections?}

\questionE{2. How are you currently using your resources---time, energy, and~finances? What's working well for~you, and~what would you like to~change?}

\questionE{3. Which resources---time, money, or~energy---do you have in~abundance, and~which ones are you lacking for~what truly matters to~you?}


\clusterWithProgram{Time and~Energy}{10–20 min}{where my~strength goes}{Resource}

\questionE{1. What do you spend most of~your time on, and~does it~benefit you?}

\questionE{2. Which activities energize you, and~how often do you engage in~them?}

\questionE{3. What activities drain your energy the~most? Can you change that?}


\clusterWithProgram{Personal Boundaries}{10–20 min}{my~"yes" and~"no"}{Personal Boundaries}

\questionE{1. Which of~your desires no longer serve you?}

\questionE{2. Which goal is it~time to~let go of---one that no longer serves you?}

\questionE{3. Which ritual or~habit would you like to~introduce or~change, and~why?}

\questionE{4. Do you feel guilty when you break your own rules?}


\clusterWithProgram{Boundaries in~relationships}{10–20 min}{where I~open up to~people}{Personal Boundaries}

\questionE{1. With which of~your close friends and~family can you allow yourself to~be vulnerable, and~with whom do you feel the~need to~appear strong?}

\questionE{2. Whom do you allow to~see your weakness and~vulnerability?}

\questionE{3. For~whom do you wear a~mask, and~why?}

\questionE{4. Who are the~people who require you to~always be at~your best? Do you want to~change this?}


\clusterWithProgram{Work Boundaries}{10–20 min}{where work ends and~I begin}{Personal Boundaries}

\questionE{1. How well do your work responsibilities align with your interests and~values?}

\questionE{2. If~you compare job rejections to~working where you're not valued, what would tip the~scales for~you?}

\questionE{3. What specifically makes you the~right person to~handle this task, and~who else could take care of~it?}

\questionE{4. When was the~last time you said no to~extra work? What stopped you from doing it~sooner?}


\clusterWithProgram{Boundaries with Technology and~Time}{10–20 min}{where my~time goes}{Personal Boundaries}

\questionE{1. When was the~last time you spent a~day without your phone or~the~internet?}

\questionE{2. Have you set boundaries for~internet use in~your life? What are they?}

\questionE{3. What did you do today to~move closer to~your main goals? And~what might have been less important?}


\clusterWithProgram{Work-Life Boundary}{10–20 min}{The~psychological boundary that separates professional responsibilities and~activities from personal life, relationships, and~leisure time. This boundary helps maintain mental health, prevents burnout, and~ensures adequate time and~energy allocation between work demands and~personal well-being.}{Personal Boundaries}

\questionE{1. Do you have a~specific time when your workday ends?}

\questionE{2. If~everything in~your life lost its meaning tomorrow, what would you regret the~most?}


\clusterWithProgram{Physical and~Bodily Boundaries}{10–20 min}{what my~body tells me}{Personal Boundaries}

\questionE{1. What physical personal boundaries do you consistently maintain, and~which ones do you often violate?}

\questionE{2. Do you love yourself enough to~let go of~what's harmful to~you?}


\clusterWithProgram{Facing Fear}{10–20 min}{what I~feel when I'm scared}{Working with Fears}

\questionE{1. Recall a~moment when you faced your fear head-on. How did you feel?}

\questionE{2. What happens to~your fear when you breathe through it? Does it~become easier?}

\questionE{3. What warm and~supportive words can you offer to~your fear?}


\clusterWithProgram{Deep Fear Analysis}{10–20 min}{what lies behind fear}{Working with Fears}

\questionE{1. If~your fear could speak, what would it~say about what it's protecting?}

\questionE{2. If~your anxiety were a~wise teacher, what would it~teach you?}

\questionE{3. Which part of~you is no longer afraid of~what used to~frighten you?}


\clusterWithProgram{Specific Fears}{10–20 min}{my~main fears}{Working with Fears}

\questionE{1. What financial concerns keep you up at~night?}

\questionE{2. What do you desire but~are afraid to~fully pursue?}

\questionE{3. Do you think others might feel awkward or~afraid when interacting with you? If~so, what do you think could be causing this?}


\clusterWithProgram{Fear and~Motivation}{10–20 min}{what fear does to~me}{Working with Fears}

\questionE{1. Does your fear motivate you to~move forward, or~does it~paralyze you?}

\questionE{2. When you avoid certain situations, what specifically frightens you about them: the~real danger, or~the~possibility of~discovering something new about yourself?}

\questionE{3. What are you avoiding so~subtly that you don't even notice it?}


\clusterWithProgram{Fear in~Relationships}{10–20 min}{intimacy scares me}{Working with Fears}

\questionE{1. Do you give people your time and~attention out of~generosity, or~from fear of~being rejected?}

\questionE{2. What scares you more: showing your vulnerability or~the~risk that it~might be used against you?}

\questionE{3. What scares you more: being alone or~facing yourself?}

\questionE{4. If~you weren't afraid of~being alone, which relationships would you end?}


\clusterWithProgram{Existential fears}{10–20 min}{what I'm truly afraid of}{Working with Fears}

\questionE{1. What do you fear more: the~intensity of~your emotions or~their complete absence?}

\questionE{2. Who will you become when you stop being afraid?}

\questionE{3. What kind of~person do you become when you choose love over fear?}


\clusterWithProgram{Unconscious fears}{10–20 min}{what I~secretly fear}{Working with Fears}

\questionE{1. What truth about yourself do you sense but~aren't ready to~face yet?}

\questionE{2. If~your closest relationships could speak, what hidden struggles would they reveal about you?}


\clusterWithProgram{Successes and~Resources in~Relationships}{10–20 min}{my~victories in~love}{Understanding Relationships}

\questionE{1. What aspect of~relationship success are you proud of?}

\questionE{2. Think of~a~relationship where you felt truly seen. What made it~special?}

\questionE{3. Consider someone who accepts you just as~you are. How do you feel when you're with them?}

\questionE{4. Consider a~relationship that helped you become a~better person. What was healing about it?}

\questionE{5. How have you helped another person? What did that bring you?}


\clusterWithProgram{Patterns and~Cycles}{10–20 min}{my~recurring mistakes}{Understanding Relationships}

\questionE{1. What patterns or~behaviors have ruined your past relationships?}

\questionE{2. Which behavioral patterns keep repeating in~your relationships?}

\questionE{3. Do you attract people who need help, or~do you choose those you can help?}

\questionE{4. Do you genuinely forgive people, or~do you pretend to~forgive them to~avoid conflict?}


\clusterWithProgram{Me~in~relationships}{10–20 min}{who I~am when I'm with others}{Understanding Relationships}

\questionE{1. Are there aspects of~your personality that you prefer not to~reveal in~relationships?}

\questionE{2. With which of~your close friends can you be vulnerable and~authentic, and~with whom do you feel the~need to~appear stronger?}

\questionE{3. Where in~your body do you feel it~when a~relationship isn't right for~you?}

\questionE{4. Do you choose intimacy with people, or~intimacy with the~image they have created of~you?}

\questionE{5. Which part of~yourself do you hide or~keep hidden in~your relationships with others?}


\clusterWithProgram{Love and~Expression}{10–20 min}{my~way of~loving}{Understanding Relationships}

\questionE{1. How do you show love to~those close to~you, and~how do you want to~receive it?}

\questionE{2. How do you express your love to~those you care about?}

\questionE{3. Do you offer people your time and~attention out of~generosity, or~is it~out of~fear of~being rejected?}


\clusterWithProgram{Influence of~Origin}{10–20 min}{what my~parents gave me}{Understanding Relationships}

\questionE{1. How do your relationships with your parents influence your romantic relationships?}

\questionE{2. What traits from the~relationships in~your childhood would you like to~keep in~your adult life, and~what would you want to~change?}

\questionE{3. How often and~meaningfully do you communicate with your close family members? Does it~enrich you?}


\clusterWithProgram{Vulnerability and~Intimacy}{10–20 min}{to~open up or~defend yourself}{Understanding Relationships}

\questionE{1. What prevents you from opening up to~those close to~you?}

\questionE{2. Do you seek understanding in~relationships, or~do you seek confirmation of~what you already think about yourself?}

\questionE{3. If~you weren't afraid of~being alone, which relationships would you end?}


\clusterWithProgram{Transformation}{10–20 min}{who am I~now}{Understanding Relationships}

\questionE{1. Who do you become when you choose love over fear?}

\questionE{2. If~your close relationships could speak, what would they reveal about what you feel you need to~hide or~protect?}


\clusterWithProgram{Triggers and~Patterns}{10–20 min}{what drains me}{Burnout  Resource}

\questionE{1. What in~your life drains your energy the~most?}

\questionE{2. When was the~last time you felt truly rested---completely, without guilt or~urgency?}

\questionE{3. What responsibilities do you assume out of~a~sense of~duty, even though they don't inspire you?}


\clusterWithProgram{Recovery --- Quick Methods}{10–20 min}{first aid for~yourself}{Burnout  Resource}

\questionE{1. What helps you quickly recover from stress and~recharge your energy?}

\questionE{2. Which activities help you restore your energy best? (music, socializing, movement, nature, creativity)}

\questionE{3. What helps you quickly relax and~restore your inner balance?}


\clusterWithProgram{Recovery --- Deep Methods}{10–20 min}{what gives me~strength}{Burnout  Resource}

\questionE{1. Which type of~rest restores you most completely: physical, emotional, creative, or~social?}

\questionE{2. What does your ideal weekend look like, and~what energizes you while providing true rest?}

\questionE{3. Who helps you recharge your energy? How do you notice feeling more alive and~vibrant when you're around them?}


\clusterWithProgram{Self-Support}{10–20 min}{how I~embrace myself}{Burnout  Resource}

\questionE{1. How do you support yourself during moments of~exhaustion or~when your energy is depleted?}

\questionE{2. What do you tell yourself when you feel burned out? Do you offer support or~criticism?}

\questionE{3. Which restorative ritual would you like to~introduce into your life?}


\clusterWithProgram{Balance and~Boundaries}{10–20 min}{what I~take and~what I~give}{Burnout  Resource}

\questionE{1. What are you willing to~give up to~make space for~recovery?}

\questionE{2. What boundaries do you need to~establish to~avoid burnout?}

\questionE{3. How would your life change if~you could rest as~much as~you work?}


\clusterWithProgram{Gratitude}{10–20 min}{what the~past has given me}{Healing the~Past}

\questionE{1. Recall a~moment when you were overwhelmed with gratitude. What sensations did you feel in~your body?}

\questionE{2. For~what can you be grateful in~your past experiences?}

\questionE{3. How have you helped someone else, and~what did you gain from it?}


\clusterWithProgram{People who helped heal}{10–20 min}{who was there for~you}{Healing the~Past}

\questionE{1. Reflect on~the~relationships that helped you become a~better person. What was healing about them?}

\questionE{2. Consider the~relationships where you felt truly seen and~accepted for~who you are. What made these connections so~special for~your healing journey?}

\questionE{3. Think of~someone who completely accepts you. What do you feel when you're with them?}

\questionE{4. With whom can you be silent and~still feel understood?}

\questionE{5. Who in~your life makes you feel safe being yourself?}


\clusterWithProgram{Forgiveness}{10–20 min}{how to~let go of~pain}{Healing the~Past}

\questionE{1. Whom haven't you forgiven yet---others or~yourself?}

\questionE{2. Do you more often genuinely forgive people, or~do you pretend to~forgive to~avoid confrontation?}

\questionE{3. If~your sadness could speak, what would it~say about your life?}

\questionE{4. What from your past are you ready to~let go of~to~make space for~what truly matters to~you now?}


\clusterWithProgram{Past Emotions}{10–20 min}{what the~body remembers}{Healing the~Past}

\questionE{1. Recall a~past emotion that brought you peace. How did it~feel in~your body?}

\questionE{2. Which emotion from your past still lingers in~your body, even if~you can't find words for~it?}

\questionE{3. What color, sound, or~image is connected to~your past emotional wound?}


\clusterWithProgram{Self-Vision}{10–20 min}{who I~really am}{Healing the~Past}

\questionE{1. What are you most proud of, and~what makes this achievement especially valuable to~you?}

\questionE{2. What achievements are you proud of? Big or~small, everything matters.}

\questionE{3. Who inspires you most, and~why?}


\clusterWithProgram{Breaking Free from the~Past}{10–20 min}{how to~let go and~move forward}{Healing the~Past}

\questionE{1. How are you feeling right now? What do you want most at~this moment?}

\questionE{2. What would you like to~make more room for~in~your life this year?}

\questionE{3. Where can you direct your energy to~bring the~greatest benefit to~both yourself and~those around you?}

\questionE{4. If~everything lost its meaning tomorrow, what would your biggest regret be?}


\clusterWithProgram{Body Signals}{10–20 min}{what my~body feels}{Body and~Emotions}

\questionE{1. What emotions do you most often notice throughout your day?}

\questionE{2. Is there an~emotion that constantly lingers in~your body, like background noise?}

\questionE{3. What happens to~your body when emotions become intense? What signals does your body send you?}

\questionE{4. What happens to~your body when you feel tired or~emotionally drained? What signals does your body send you?}


\clusterWithProgram{Emotions and~Masks}{10–20 min}{my~true feelings}{Body and~Emotions}

\questionE{1. What emotions do you experience when you're alone that you don't show to~others?}

\questionE{2. Do you use humor or~sarcasm to~express or~hide your feelings?}

\questionE{3. When someone asks, what are you feeling? Is your first impulse to~answer honestly or~to~say what they expect to~hear?}

\questionE{4. What part of~yourself are you hiding in~your body by~physically tensing your muscles or~freezing?}


\clusterWithProgram{Attitude towards feelings}{10–20 min}{what I~am feeling right now}{Body and~Emotions}

\questionE{1. Do you allow yourself to~simply feel what's there, or~do you often think you should be feeling something else?}

\questionE{2. What kind and~compassionate words can you offer your emotions instead of~criticism?}

\questionE{3. What mood would you like to~create for~yourself in~the~morning? How might this feel in~your body?}


\clusterWithProgram{Deep Layers}{10–20 min}{what my~body tells me}{Body and~Emotions}

\questionE{1. If~your anxiety were a~wise teacher, what might it~be trying to~teach you?}

\questionE{2. What are your regular feelings telling you?}

\questionE{3. What gentle and~kind feelings can you cultivate toward yourself right now?}


\clusterWithProgram{Relationship with Money and~Self-Worth}{10–20 min}{my~money and~me}{Money and~Self-Worth}

\questionE{1. What influences your sense of~deserving financial well-being?}

\questionE{2. Do you believe that you're not good enough for~money? Where does this belief come from?}

\questionE{3. What would you do in~life if~money were no longer a~limitation?}


\clusterWithProgram{Financial Fears}{10–20 min}{what I~fear about money}{Money and~Self-Worth}

\questionE{1. What financial worries keep you up at~night?}

\questionE{2. What are you more afraid of: financial failure or~success that would change everything about your life?}

\questionE{3. If~money disappeared, what would you lose besides the~money itself?}


\clusterWithProgram{Dreams and~Motivation}{10–20 min}{what I~dream of~buying}{Money and~Self-Worth}

\questionE{1. What do you envision when you dream of~financial freedom?}

\questionE{2. What would you do if~you had enough money to~pursue any plans you wanted?}

\questionE{3. If~you had all the~necessary resources---time, money, and~opportunities---what would you want to~do?}


\clusterWithProgram{Goals and~Strategy}{10–20 min}{where I~want to~get to}{Money and~Self-Worth}

\questionE{1. What specific financial goal do you want to~achieve within the~year?}

\questionE{2. What financial goals would you like to~achieve in~five years?}

\questionE{3. Who can help you with your financial development: a~mentor, a~book, or~a~course?}

\questionE{4. What is the~first concrete step you can take this week to~move closer to~your financial goals?}


\clusterWithProgram{Wisdom from Mistakes}{10–20 min}{what life has taught me}{Crisis 27 / 45}

\questionE{1. What wisdom can be found in~your mistakes?}

\questionE{2. What are the~three most important life lessons you would pass on~to those who come after you?}

\questionE{3. If~you could change something in~your past, what would it~be?}

\questionE{4. For~what are you grateful to~your younger self?}


\clusterWithProgram{Reevaluation of~Values}{10–20 min}{what has become most important}{Crisis 27 / 45}

\questionE{1. Which values used to~seem important to~you but~have now lost their significance?}

\questionE{2. Which values have become more important to~you than before?}

\questionE{3. If~you could live the~next 10 years differently, what would you change in~your priorities and~why?}


\clusterWithProgram{Possibility of~Change}{10–20 min}{what is within my~power}{Crisis 27 / 45}

\questionE{1. Are there aspects of~your life you want to~radically change?}

\questionE{2. What's stopping you from making the~changes you want?}

\questionE{3. What would you be willing to~give up to~transform your life?}

\questionE{4. If~you knew everything would work out, what changes would you dare to~make in~your life?}


\clusterWithProgram{Professional Identity}{10–20 min}{what I~work as~and take pride in}{AI Anxiety and~the~Future of~Work}

\questionE{1. Who are you professionally beyond your technical skills? What defines you as~a~professional?}

\questionE{2. What sets you apart from others in~your field?}

\questionE{3. What skills or~qualities do you possess that could become especially valuable in~a~world where technology is transforming the~professional landscape?}


\clusterWithProgram{Signs of~Anxiety}{10–20 min}{Do I~like my~work?}{AI Anxiety and~the~Future of~Work}

\questionE{1. Which concerns you more: the~possibility of~losing your job or~becoming professionally irrelevant?}

\questionE{2. How often do you feel professional anxiety about AI and~technology?}

\questionE{3. What situations at~work intensify your fear of~inadequacy?}

\questionE{4. What methods do you typically use to~cope with the~fear of~professional inadequacy?}


\clusterWithProgram{Retraining and~Development}{10–20 min}{how I~learn new things}{AI Anxiety and~the~Future of~Work}

\questionE{1. How many hours a~week do you dedicate to~reskilling and~professional development?}

\questionE{2. What new skills or~qualities do you want to~develop in~the~coming year to~feel more confident in~a~changing world?}

\questionE{3. Do you have a~professional development plan in~place if~your current role becomes automated?}

\questionE{4. Which person, mentor, or~community could help you develop your skills in~working with new technologies?}


\clusterWithProgram{Job Market and~Opportunities}{10–20 min}{new opportunities for~me}{AI Anxiety and~the~Future of~Work}

\questionE{1. Which new professional niches are emerging due to~AI and~automation?}

\questionE{2. How can you use AI as~an~ally to~enhance your professional expertise?}

\questionE{3. Which colleagues or~peers in~your field have successfully adapted to~new technologies? What can you learn from them?}


\clusterWithProgram{Feelings and~Signals}{10–20 min}{how I~feel}{Info-obesity}

\questionE{1. What happens to~your body when your screen floods with notifications, and~what signals does it~send you?}

\questionE{2. What emotions arise after an~hour in~the~information stream: calmness, confusion, or~overload?}

\questionE{3. When you feel the~urge to~check something on~your phone or~computer, what do you actually need at~that moment?}


\clusterWithProgram{Fears and~Motives}{10–20 min}{what I~fear and~desire}{Info-obesity}

\questionE{1. What are you afraid of~missing in~your information feed?}

\questionE{2. If~you stopped checking the~news for~a~week, what would you lose? What would you gain?}

\questionE{3. How does your digital consumption help you avoid things like boredom, loneliness, or~self-reflection?}


\clusterWithProgram{Boundary and~Saturation}{10–20 min}{when there's enough information}{Info-obesity}

\questionE{1. Where do you draw the~line between staying well-informed and~experiencing information overload?}

\questionE{2. How much information do you truly need in~a~day? How do you know when you've had enough?}

\questionE{3. Which content is genuinely useful to~you, and~which do you consume on~autopilot?}


\clusterWithProgram{From Consumption to~Creation}{10–20 min}{how to~become a~creator}{Info-obesity}

\questionE{1. What would happen if~you stopped merely consuming and~started creating instead?}

\questionE{2. What content or~idea would you like to~create instead of~endlessly consuming?}

\questionE{3. How often do you write, draw, or~create something of~your own compared to~the~time you spend consuming content?}


\clusterWithProgram{Identity without digits}{10–20 min}{my~real face}{Info-obesity}

\questionE{1. How do you perceive yourself without your digital footprint, ratings, and~likes?}

\questionE{2. What aspects of~your personality do you reveal online, and~which do you keep hidden?}

\questionE{3. If~all your digital accounts disappeared tomorrow, what would change about who you are?}


\clusterWithProgram{Independence}{10–20 min}{who am I~without the~internet}{Info-obesity}

\questionE{1. Can you spend a~day without your smartphone? How does that make you feel?}

\questionE{2. When was the~last time you deeply reflected on~something, relying solely on~your own thoughts?}

\questionE{3. What decision have you made in~the~last month based solely on~your own experience, without consulting Google or~the~internet?}


\clusterWithProgram{Information trap}{10–20 min}{when I~stop trying}{Learned Helplessness 2.0}

\questionE{1. Which news sources and~information feeds are shaping your worldview?}

\questionE{2. How much time do you spend each day consuming information that paralyzes you?}

\questionE{3. Whose views and~beliefs do you adopt as~your own without checking if~they truly align with your personal experience?}


\clusterWithProgram{Fears and~Choice}{10–20 min}{what stops me}{Learned Helplessness 2.0}

\questionE{1. What are you more afraid of---failure or~inaction?}

\questionE{2. What does your inner critic tell you that you can't do? Where do you think these beliefs originated?}

\questionE{3. What hope have you already given up on, and~do you want to~reclaim it?}


\clusterWithProgram{Illusion of~Control}{10–20 min}{what I~want to~hold in~my hands}{Learned Helplessness 2.0}

\questionE{1. What would happen if~you stopped trying to~control what is beyond your control?}

\questionE{2. In~which areas of~your life do you feel you're striving to~make a~change, but~the~results remain unchanged?}

\questionE{3. If~you focused only on~what is truly within your control, how would this change your attitude toward life?}


\clusterWithProgram{Personality Parts and~Resistance}{10–20 min}{who inside me~is afraid}{Learned Helplessness 2.0}

\questionE{1. Which part of~you is afraid to~take action? What is it~protecting?}

\questionE{2. What do you gain from remaining helpless? What does inaction provide you?}

\questionE{3. If~one part of~you was afraid while another part was ready to~take action, what would that ready part say?}


\clusterWithProgram{Competence and~Success History}{10–20 min}{what I'm good at}{Learned Helplessness 2.0}

\questionE{1. When was the~last time you felt competent and~capable of~making a~difference?}

\questionE{2. What small actions or~habits have helped you achieve results?}

\questionE{3. In~which area of~your life do you feel most influential and~capable?}


\clusterWithProgram{From Helplessness to~Agency}{10–20 min}{where success leads me}{Learned Helplessness 2.0}

\questionE{1. Who are you when you're not paralyzed by~helplessness?}

\questionE{2. What decisions can you make today to~feel more in~control of~your life?}

\questionE{3. If~you took full responsibility for~the~aspects of~your life within your control, how might this change your decisions and~actions?}


\clusterWithProgram{Sources of~Closeness}{10–20 min}{who supports me}{Parasocial Dependency}

\questionE{1. Who among the~real people in~your life gives you the~most emotional support?}

\questionE{2. Which influencer, character, or~AI makes you feel supported? What is it~about them specifically?}

\questionE{3. What needs for~closeness and~understanding are fulfilled by~interacting with virtual companions for~you?}

\questionE{4. What genuine need does virtual content fulfill for~you?}


\clusterWithProgram{Escape and~Avoidance}{10–20 min}{what I~avoid in~life}{Parasocial Dependency}

\questionE{1. What are you running from when you fall into endless scrolling?}

\questionE{2. What does virtuality replace for~you in~terms of~real human touch and~intimacy?}

\questionE{3. Which real people or~situations are you avoiding through the~screen?}

\questionE{4. If~you disconnected from all virtual relationships for~a~week, what would you miss?}


\clusterWithProgram{The~Proximity Paradox}{10–20 min}{when the~screen is closer than people}{Parasocial Dependency}

\questionE{1. Why do virtual relationships seem easier to~you than real ones?}

\questionE{2. What advantages do virtual relationships offer you?}

\questionE{3. What risks and~challenges accompany virtual intimacy?}


\clusterWithProgram{Authentic Self}{10–20 min}{my~true face}{Parasocial Dependency}

\questionE{1. When was the~last time you felt genuine closeness---without a~screen, without filters?}

\questionE{2. Who are you when no one sees your posts, likes, or~online status?}

\questionE{3. What aspects of~yourself do you reveal online but~conceal in~face-to-face interactions?}

\questionE{4. If~all your virtual relationships disappeared tomorrow, would anything change about who you truly are?}


\clusterWithProgram{Authenticity Recovery}{10–20 min}{returning to~my true self}{Parasocial Dependency}

\questionE{1. What needs to~change in~your life to~cultivate more authentic relationships?}

\questionE{2. What genuine human connections can you cultivate to~meet real needs?}

\questionE{3. To~whom in~your life would you like to~share the~thoughts you usually keep for~online conversations?}

\questionE{4. What step could you take today to~meaningfully reconnect with someone who matters to~you?}


\clusterWithProgram{Fatigue and~Triggers}{10–20 min}{what drains my~energy}{Hybrid Life --- Remote Work}

\questionE{1. How many virtual meetings per week start to~drain your internal resources?}

\questionE{2. What happens to~your body when you feel tired? What signals does it~send?}

\questionE{3. Which digital habits have become invisible chains for~you?}

\questionE{4. How do your body and~mind signal that you are overworked?}


\clusterWithProgram{Sacrifices and~Priorities}{10–20 min}{what I'm giving up}{Hybrid Life --- Remote Work}

\questionE{1. What are you sacrificing by~spending more and~more time in~the~digital world?}

\questionE{2. What important things in~your life are you neglecting because of~work?}

\questionE{3. How much energy do you spend maintaining your professional facade in~different situations?}


\clusterWithProgram{Boundaries}{10–20 min}{when there's enough information}{Hybrid Life --- Remote Work}

\questionE{1. What are your current boundaries between work and~personal life?}

\questionE{2. What would happen if~you turned off notifications after 6 p.m.?}

\questionE{3. What ritual or~routine signifies your transition from work to~personal life?}

\questionE{4. How do the~people close to~you feel about your constant online presence?}


\clusterWithProgram{Role Separation}{10–20 min}{what's mine and~what's work}{Hybrid Life --- Remote Work}

\questionE{1. Where does your professional role end, and~where does your personal identity begin?}

\questionE{2. How do you transition from worker to~person at~home?}

\questionE{3. What aspects of~yourself do you not reveal at~work?}


\clusterWithProgram{Identity and~Digital Footprint}{10–20 min}{my~online and~offline image}{Hybrid Life --- Remote Work}

\questionE{1. Who are you when you turn off all notifications and~put your phone away?}

\questionE{2. Which version of~yourself do you present in~the~online world, and~what remains behind the~scenes?}

\questionE{3. If~you lost internet access for~a~week starting tomorrow, who would you discover yourself to~be?}


\clusterWithProgram{Hybrid Opportunities}{10–20 min}{my~advantages today}{Hybrid Life --- Remote Work}

\questionE{1. What advantages of~hybrid living do you already value?}

\questionE{2. How can you better leverage the~opportunities of~a~hybrid lifestyle for~personal development?}

\questionE{3. What freedoms has remote work brought into your life?}


\clusterWithProgram{Content and~Authenticity}{10–20 min}{my~posts and~me}{Authenticity vs Algorithms}

\questionE{1. What content do you create out of~boredom, social pressure, or~the~desire to~be liked?}

\questionE{2. What content do you create genuinely, from the~heart?}

\questionE{3. How does your online personality differ from your real-life self?}


\clusterWithProgram{Authenticity Risks}{10–20 min}{what I~fear in~myself}{Authenticity vs Algorithms}

\questionE{1. Which aspects of~your personality become invisible in~the~digital space?}

\questionE{2. Which part of~yourself do you hide out of~fear of~judgment?}

\questionE{3. What makes showing your true emotions online feel risky to~you?}

\questionE{4. What people or~situations cause you to~wear a~mask?}


\clusterWithProgram{The~Boundary Between Presentation and~Censorship}{10–20 min}{when there is enough information}{Authenticity vs Algorithms}

\questionE{1. Where do you draw the~line between healthy self-presentation and~self-censorship?}

\questionE{2. What aspects of~your life do you prefer to~keep private, and~what influences this decision?}

\questionE{3. Do you have people or~communities where you can be completely yourself?}


\clusterWithProgram{Choice between acceptance and~authenticity}{10–20 min}{to~be yourself or~to~be liked}{Authenticity vs Algorithms}

\questionE{1. How do you choose between authenticity and~acceptance?}

\questionE{2. What content would you create if~there were no likes or~ratings?}

\questionE{3. If~you were completely anonymous online, who would you be?}


\clusterWithProgram{Authenticity in~the~Age of~Algorithms}{10–20 min}{my~true face}{Authenticity vs Algorithms}

\questionE{1. Where is your authenticity right now---online or~offline?}

\questionE{2. Which parts of~you feel authentic and~don't need any filter?}

\questionE{3. If~your online version and~your real-life version could meet, what would they say to~each other?}


\clusterWithProgram{Authenticity Recovery}{10–20 min}{how to~find your true self}{Authenticity vs Algorithms}

\questionE{1. Which aspect of~yourself are you ready to~reveal more openly?}

\questionE{2. With whom would you want to~share your authentic self? Who are these people?}

\questionE{3. What authentic piece of~content would you create if~you weren't afraid?}


\clusterWithProgram{Guilt and~Responsibility}{10–20 min}{Do I~like my~work?}{Eco-guilt and~Climate Anxiety}

\questionE{1. How much energy do you spend on~eco-guilt rather than taking action?}

\questionE{2. Which scares you more: the~discomfort of~changing your lifestyle or~the~consequences of~the~climate crisis?}

\questionE{3. Where does personal responsibility end and~systemic responsibility begin?}

\questionE{4. How often do you find yourself paralyzed by~guilt instead of~taking action?}


\clusterWithProgram{Emotions and~Denial}{10–20 min}{what I~hide from myself}{Eco-guilt and~Climate Anxiety}

\questionE{1. What pain regarding nature and~its suffering are you suppressing within yourself?}

\questionE{2. When was the~last time you allowed yourself to~experience climate anxiety without judgment?}

\questionE{3. What do you rationalize or~deny regarding environmental issues?}


\clusterWithProgram{Personal Choice}{10–20 min}{what is in~my hands}{Eco-guilt and~Climate Anxiety}

\questionE{1. What is one personal choice you can make that truly makes a~difference?}

\questionE{2. What small actions are you already taking, and~do they have value?}

\questionE{3. If~you knew for~certain that your actions would help the~planet, what would you change in~your life?}


\clusterWithProgram{Identity and~System}{10–20 min}{my~place in~the~world}{Eco-guilt and~Climate Anxiety}

\questionE{1. Who are you beyond your consumer choices?}

\questionE{2. How do the~system---encompassing corporations, government, and~the~economy---influence your choices?}

\questionE{3. Can you be environmentally conscious within a~non-ecological system? How?}


\clusterWithProgram{From Guilt to~Action}{10–20 min}{what I~do for~the~planet}{Eco-guilt and~Climate Anxiety}

\questionE{1. From what eco-guilt are you ready to~release yourself?}

\questionE{2. What small action can you incorporate into your life starting today to~feel more whole and~complete in~ecological matters?}

\questionE{3. Who or~what can support you in~making environmentally friendly choices?}

\questionE{4. How will you track your progress---by materials/content or~by~your inner sense?}


\clusterWithProgram{Attribution of~Merit}{10–20 min}{my~achievements or~luck}{Impostor Syndrome in~the~LinkedIn Era}

\questionE{1. How often do you attribute your successes to~just getting lucky, coincidence, or~the~help of~the~team?}

\questionE{2. List three undeniable facts about your career, including numbers or~completed projects.}

\questionE{3. What achievements are you genuinely proud of, even if~no one liked your post?}


\clusterWithProgram{Disconnect from Reality}{10–20 min}{my~social media mask}{Impostor Syndrome in~the~LinkedIn Era}

\questionE{1. Compare your public profile (resume) with your internal sense of~self---how big is the~gap?}

\questionE{2. Which professional insecurity do you prefer to~keep to~yourself rather than discuss with colleagues?}

\questionE{3. What's the~worst thing that could happen if~you said, I~don't know the~answer to~that question?}


\clusterWithProgram{Value and~Identity}{10–20 min}{what matters to~me}{Impostor Syndrome in~the~LinkedIn Era}

\questionE{1. How do you most often think about yourself---through your achievements (I'm the~person who did this) or~through your inherent qualities (I'm this kind of~person)?}

\questionE{2. Who are you without your job titles, projects, and~professional positions?}

\questionE{3. How can you find fulfillment in~the~process of~working toward your goals, not just at~the~moment you achieve them?}


\clusterWithProgram{Monster Analysis}{10–20 min}{my~main fears}{Sunday Anxiety}

\questionE{1. Which specific event or~task coming up this week is causing you the~most stress?}

\questionE{2. Is this tension due to~a~fear of~not coping, boredom, or~dealing with unpleasant people?}

\questionE{3. On~a~scale of~1 to~10, how satisfied are you with your overall work?}

\questionE{4. Is there a~real threat in~what's worrying you, or~is it~just a~pattern of~worry?}


\clusterWithProgram{Boundaries and~Resources}{10–20 min}{what will help me}{Sunday Anxiety}

\questionE{1. What is the~kindest and~most caring thing you can do for~yourself right now?}

\questionE{2. What small ritual tomorrow morning will help you start your day more gently?}

\questionE{3. Who or~what can support you this week?}


\clusterWithProgram{Anatomy of~Guilt}{10–20 min}{what is happening to~me}{Parental Guilt Over Screen Time}

\questionE{1. What do you feel in~the~moment when you hand your child the~tablet: relief, irritation, or~shame?}

\questionE{2. What is your deepest fear when you think about your child's screen time?}

\questionE{3. Do you believe that a~good parent should entertain their child 24/7 without any help from devices?}


\clusterWithProgram{Social Mirror}{10–20 min}{what other people think}{Cryptocurrency FOMO}

\questionE{1. Whose success in~crypto triggers complicated feelings in~you? Who do you follow?}

\questionE{2. Do you believe that others are making money easily and~quickly while you're missing out on~opportunities?}

\questionE{3. Which feeling is stronger: the~joy from your profits or~the~frustration that you could have made more?}


\clusterWithProgram{Magical Thinking}{10–20 min}{my~dreams of~easy money}{Cryptocurrency FOMO}

\questionE{1. Did you get into crypto to~preserve your capital or~to~quickly transform your life and~escape from reality?}

\questionE{2. Do you approach crypto investing as~a~calculated strategy or~a~form of~gambling?}

\questionE{3. What gives you the~feeling of~being "in the~market"---a connection to~the~future, excitement, or~a~sense of~superiority?}


\clusterWithProgram{Identity}{10–20 min}{who am I~without the~hype}{Cryptocurrency FOMO}

\questionE{1. Who are you without your digital assets and~virtual achievements?}

\questionE{2. If~the~entire crypto market disappeared tomorrow, what solid skills and~real values would you still retain?}



\newpage
\thispagestyle{empty}
\vspace*{0.3\textheight}

{\centering\sffamily\bfseries\fontsize{18pt}{22pt}\selectfont Attention: Deep Work Ahead\par}

\vspace{2em}

The following section requires special care.

Before continuing, make sure:

\begin{itemize}
\item You are in a safe place
\item You have time and energy
\item No one will disturb you
\end{itemize}

\vspace{1em}

These questions may evoke strong emotions. That's normal---it means you're touching something important.

If it becomes too overwhelming---stop. Take a break. Return later.

\vspace{2em}
{\centering\itshape Be gentle with yourself.\par}

\newpage

\part{Part III: Deep Work}
\partsubtitle{Transformation --- integrating discoveries}
\programbreak

\clusterWithProgram{Pride and~Meaning}{15–30 min}{what I~am proud of}{Think About Life}

\questionI{1. What are you proudest of?}

\questionI{2. If~you had only one year left to~live, how would you spend it?}

\questionI{3. If~everything lost its meaning tomorrow, what would you regret the~most?}


\clusterWithProgram{Vision of~the~Future}{15–30 min}{who I~want to~become}{Think About Life}

\questionI{1. Imagine your future self---the person you aspire to~become in~what matters most to~you. What advice would that version of~you give to~your current self?}

\questionI{2. If~your parents could truly see you, what would they understand?}

\questionI{3. What do you want most right now?}


\clusterWithProgram{Business Metrics (for Entrepreneurs)}{15–30 min}{A~psychological cluster focused on~developing analytical thinking and~data-driven decision-making skills essential for~successful entrepreneurship. Helps entrepreneurs understand key performance indicators, financial metrics, and~business analytics to~optimize their ventures and~make informed strategic decisions.}{Think About Career or~Business}

\questionI{1. What is the~cost of~acquiring one new customer for~your business?}

\questionI{2. Which key performance indicator (KPI) do you track in~your business?}


\clusterWithProgram{The~Meaning of~Health}{15–30 min}{why do I~need to~be healthy}{Think About Health}

\questionI{1. Why is having good health important to~you? What does it~provide for~you?}

\questionI{2. If~you had perfect health, what would change in~your life?}


\clusterWithProgram{Future Health}{15–30 min}{where I~want to~get to}{Think About Health}

\questionI{1. What changes in~your health would you like to~see in~your life a~year from now?}

\questionI{2. Where do you see yourself health-wise in~one year? How will you feel?}

\questionI{3. What kind of~rest do your body and~soul need? Where and~how would you like to~recharge your energy?}


\clusterWithProgram{Ideal Future}{15–30 min}{who I~want to~become}{Know Yourself}

\questionI{1. Describe your ideal relaxation day: Where would you be, who would you be with, and~what would you be doing?}

\questionI{2. Imagine you've changed the~world for~the~better. What specifically has changed because of~you?}

\questionI{3. If~you knew you couldn't fail, what would you do?}


\clusterWithProgram{Development and~Path}{15–30 min}{where I'm growing towards}{Know Yourself}

\questionI{1. What do you want to~learn first and~foremost, and~why is it~important to~you at~this moment?}

\questionI{2. Where in~the~world would you like to~go, and~what draws you there?}

\questionI{3. What skill or~quality would you like to~develop over the~next year?}


\clusterWithProgram{Mood as~a~Choice}{15–30 min}{How to~manage your mood}{Improve Emotional State}

\questionI{1. What kind of~mood would you like to~set for~yourself in~the~morning before your day begins?}

\questionI{2. How do you regain balance when emotions overwhelm you?}


\clusterWithProgram{Achievements and~Pride}{15–30 min}{what I~am proud of}{Reviewing Goals}

\questionI{1. What are your most proud achievements?}

\questionI{2. Which achievement surprised you the~most---something you didn't expect you could accomplish?}


\clusterWithProgram{Action}{15–30 min}{my~action plan}{Reviewing Goals}

\questionI{1. What specific step can you take this week to~get closer to~your main goal?}

\questionI{2. Who or~what could help you get closer to~this goal? What resources and~support do you need?}


\clusterWithProgram{Action}{15–30 min}{my~first step today}{Dreamers}

\questionI{1. What specific step can you take this week to~get closer to~your dream?}

\questionI{2. If~you don't take action, how do you envision your life in~a~few years? What would be your most painful regret?}

\questionI{3. When would you like to~start? Is there a~suitable day this week?}


\clusterWithProgram{Continuing the~Path}{15–30 min}{where I'm going now}{Reflection}

\questionI{1. What question should you ask yourself regularly?}

\questionI{2. When will you engage in~self-reflection again? In~a~month, a~quarter, or~a~year?}


\clusterWithProgram{Transformation}{15–30 min}{how I~change}{3 Pillars of~Purification}

\questionI{1. When was the~last time your growth came not through achievements, but~through accepting and~letting go of~what wasn't working?}

\questionI{2. What new aspects of~yourself have you discovered through this cleansing process?}

\questionI{3. What have you become after this cycle of~purification, and~what has changed within you?}


\clusterWithProgram{Integration}{15–30 min}{what will change in~life}{3 Pillars of~Purification}

\questionI{1. How could this new understanding impact your decisions both in~the~near and~distant future?}

\questionI{2. What concrete step are you ready to~take today, building on~this purification?}

\questionI{3. What new knowledge or~skills could enhance your purification experience and~make it~more integrated?}


\clusterWithProgram{Resource Development}{15–30 min}{how to~become stronger}{Resource}

\questionI{1. Which resource would you like to~develop first?}

\questionI{2. What steps should you take to~gain access to~new resources?}

\questionI{3. To~whom or~what can you turn to~expand your opportunities for~growth?}


\clusterWithProgram{Action}{15–30 min}{my~first steps}{Personal Boundaries}

\questionI{1. What boundary do you want to~establish in~the~next month?}

\questionI{2. How would you know if~this boundary is working? What signs would indicate this?}

\questionI{3. Whom would you ask to~support you in~establishing this boundary?}


\clusterWithProgram{Action}{15–30 min}{what I~am doing now}{Working with Fears}

\questionI{1. What small step could you take toward addressing what's troubling you?}

\questionI{2. Who or~what resource could assist you in~this work?}


\clusterWithProgram{Action}{15–30 min}{what I~will do next}{Understanding Relationships}

\questionI{1. How can you improve your relationship with someone close to~you? What is the~first step you are ready to~take?}

\questionI{2. With whom are you ready to~share something more personal about yourself this week?}

\questionI{3. What qualities do you want to~develop in~yourself for~closer, more trusting relationships?}


\clusterWithProgram{Action}{15–30 min}{my~first steps}{Burnout  Resource}

\questionI{1. What recovery ritual can you introduce this week?}

\questionI{2. To~whom will you disclose your burnout and~seek support?}

\questionI{3. If~you had an~entire day of~unrestricted rest, how would you spend it?}


\clusterWithProgram{Personal Identity Reframing}{15–30 min}{Who am I~after everything I've been through}{Healing the~Past}

\questionI{1. Who would you be if~you stopped trying to~meet others' expectations?}

\questionI{2. If~no one knew you and~you could start with a~blank slate, who would you choose to~be?}

\questionI{3. If~there were no social expectations or~limitations, what part of~yourself would you allow to~express more freely?}

\questionI{4. If~you could be completely honest for~one day, what would you say?}


\clusterWithProgram{Action and~Future}{15–30 min}{my~steps after pain}{Healing the~Past}

\questionI{1. What is the~simplest first step you can take to~integrate this lesson from your past into your life?}

\questionI{2. Whom would you like to~share your healing journey with? Who are the~people for~whom your story matters?}


\clusterWithProgram{Body Regulation}{15–30 min}{how the~body heals me}{Body and~Emotions}

\questionI{1. How can you help your body manage intense emotions?}

\questionI{2. What movements or~touches help you find your center again?}

\questionI{3. Do you notice how your breathing changes with different emotions? What happens to~your body when you feel anxious or~joyful?}


\clusterWithProgram{Success and~Transformation}{15–30 min}{where success leads me}{Money and~Self-Worth}

\questionI{1. What would you pursue if~you knew you couldn't fail?}

\questionI{2. How would your life change if~you achieved financial freedom?}


\clusterWithProgram{New Meaning}{15–30 min}{who am I~now}{Crisis 27 / 45}

\questionI{1. How do you see yourself in~10 to~15 years? Imagine and~describe an~ordinary day in~that future life.}

\questionI{2. How do you want to~reinvent yourself?}

\questionI{3. What new purpose in~life is emerging for~you after the~crisis?}


\clusterWithProgram{Action and~Transition}{15–30 min}{my~path out of~crisis}{Crisis 27 / 45}

\questionI{1. What specific step can you take this week to~begin your transition?}

\questionI{2. Whom will you tell about your crisis and~seek support from?}


\clusterWithProgram{Rethinking Work}{15–30 min}{how I~see work}{AI Anxiety and~the~Future of~Work}

\questionI{1. If~AI could do your job, what would you want to~do instead? What unique value could you bring to~the~world?}

\questionI{2. If~you had to~start your career over from scratch right now, what would you study?}

\questionI{3. What professional qualities or~experiences do you prefer to~keep private? What remains out of~the~spotlight in~your professional persona?}


\clusterWithProgram{Action and~Strategy}{15–30 min}{my~action plan}{AI Anxiety and~the~Future of~Work}

\questionI{1. What is the~first concrete step you will take this week to~better prepare yourself for~the~changes in~the~world of~work?}

\questionI{2. What new skill or~knowledge do you want to~acquire in~the~next three months?}

\questionI{3. How will you track your progress in~adapting to~professional changes?}


\clusterWithProgram{Action and~Balance}{15–30 min}{my~first steps}{Info-obesity}

\questionI{1. What specific digital boundary will you set for~yourself this week?}

\questionI{2. Which app or~habit are you willing to~delete or~limit?}

\questionI{3. Which offline activity would you like to~reintroduce into your life?}

\questionI{4. How will you track your progress in~achieving digital balance?}


\clusterWithProgram{Action}{15–30 min}{first steps towards change}{Learned Helplessness 2.0}

\questionI{1. What specific step can you take today to~feel more confident in~your abilities?}

\questionI{2. What habitual worry are you ready to~let go of~this week?}

\questionI{3. What new habit will you adopt to~enhance your sense of~competence?}


\clusterWithProgram{Boundaries and~Balance}{15–30 min}{how not to~get lost online}{Parasocial Dependency}

\questionI{1. Which virtual relationships or~content should you keep because they genuinely help you?}

\questionI{2. How can you enjoy the~internet while maintaining your authentic connections?}

\questionI{3. What boundaries do you want to~establish for~yourself between the~online and~offline worlds?}


\clusterWithProgram{Action and~Integration}{15–30 min}{how I~will put it~all together}{Hybrid Life --- Remote Work}

\questionI{1. What boundary will you set this week between work and~your personal life?}

\questionI{2. What "switching off" ritual will you incorporate into your day?}

\questionI{3. How will you know when your balance is restored?}


\clusterWithProgram{Action and~Balance}{15–30 min}{how to~be yourself online}{Authenticity vs Algorithms}

\questionI{1. What truth about yourself are you ready to~accept right now?}

\questionI{2. How will you measure your authenticity: by~likes or~by~your inner sense?}

\questionI{3. What digital detox ritual could you introduce into your life?}


\clusterWithProgram{Activism and~Consistency}{15–30 min}{what I~do for~the~planet}{Eco-guilt and~Climate Anxiety}

\questionI{1. Is there an~environmental cause that inspires you, and~why?}

\questionI{2. How would you like to~participate: through personal actions, educating others, or~activism?}

\questionI{3. What role would you like to~play in~creating a~healthier world?}

\questionI{4. What achievements make you proud? What in~your life fills you with a~sense of~pride?}

\questionI{5. Which achievements are you most proud of?}

\questionI{6. How can you derive even more pleasure from the~process of~achieving your environmental goals?}

\questionI{7. What is inherently valuable about you, independent of~your environmental actions and~achievements?}


\clusterWithProgram{Breaking Free from the~Race}{15–30 min}{how to~live without comparisons}{Impostor Syndrome in~the~LinkedIn Era}

\questionI{1. Whose opinion or~approval do you still need to~feel like a~genuine professional?}

\questionI{2. What advice would you give to~a~friend if~they felt as~insecure as~you do right now?}

\questionI{3. What are you ready to~do today, knowing you're good enough for~it?}

\questionI{4. Which field consumes most of~your time and~energy right now?}

\questionI{5. Why do I~believe this will work? What is my~confidence in~this path based on? Is there a~more effective way? How can I~find out?}

\questionI{6. If~you could choose without any limitations, where would you want to~work?}

\questionI{7. Which is more painful for~you right now: getting rejected in~job interviews or~continuing to~work where your worth isn't recognized?}

\questionI{8. Do you criticize yourself for~resting, even when you have a~lot of~work and~responsibilities?}

\questionI{9. How long would your savings last if~you decided to~take a~break from work?}

\questionI{10. How does your current job help you achieve what truly matters to~you?}

\questionI{11. Which aspects of~your current job don't align with the~goals that truly matter to~you?}

\questionI{12. How much satisfaction does your current job bring you? Rate it~on~a~scale of~1 to~10.}

\questionI{13. What would your ideal job be?}


\clusterWithProgram{Global Reality Check}{15–30 min}{when anxiety doesn't let go}{Sunday Anxiety}

\questionI{1. Consider whether the~fear of~change outweighs the~pain of~working somewhere you're not valued --- which feels heavier right now?}

\questionI{2. Your dream job --- is there room for~Sunday blues?}

\questionI{3. What step will you take this week to~bring your reality a~little closer to~that dream?}

\questionI{4. If~your Sunday anxiety could speak, what would it~be trying to~tell you about your life?}

\questionI{5. Will you still feel this way every Sunday five years from now?}

\questionI{6. What needs to~change in~your life for~Sunday to~be just Sunday again?}


\clusterWithProgram{Hidden Meanings}{15–30 min}{what lies behind the~guilt}{Parental Guilt Over Screen Time}

\questionI{1. What anxiety of~your own are you trying to~soothe when you take away devices or~get angry about them?}

\questionI{2. Reflecting on~your childhood, what did you lack that you are now trying to~compensate for~or~prohibit for~your child?}

\questionI{3. What is truly driving your arguments with your child about phone time? Could it~be your way of~connecting when you can't find other reasons to~talk?}


\clusterWithProgram{Digital Bridge}{15–30 min}{what to~do next}{Parental Guilt Over Screen Time}

\questionI{1. What if~the~screen isn't a~wall between you but~a~door? How can you walk through that door together with your child?}

\questionI{2. Who will you become for~your child if~you stop being a~censor and~become a~guide in~the~digital world?}

\questionI{3. What is one gadget-free family ritual you could introduce that would bring genuine joy to~both of~you, rather than feeling like a~healthy obligation?}

\questionI{4. How much time do you spend each day monitoring cryptocurrency charts?}

\questionI{5. Which channels and~bloggers influence your investment decisions?}

\questionI{6. What beliefs about money and~technology influence your decisions when purchasing gadgets for~your child?}

\questionI{7. What is truly driving your desire to~make quick money?}

\questionI{8. What inner voids are you trying to~fill by~chasing cryptocurrency trends?}

\questionI{9. What uncomfortable feelings about yourself are you avoiding by~spending time on~your phone?}

\questionI{10. Which aspect of~your vulnerability are you concealing behind your digital habits?}

\questionI{11. Who are you without screens, notifications, and~digital achievements?}


\clusterWithProgram{Crypto Detox}{15–30 min}{how to~stop tracking}{Cryptocurrency FOMO}

\questionI{1. How much money are you willing to~lose without regret and~without it~affecting your quality of~life? (Assess your true risk tolerance)}

\questionI{2. Which digital wellness rules are you ready to~implement to~reclaim your peaceful sleep?}



\newpage
\thispagestyle{empty}
\vspace*{0.2\textheight}

{\centering\sffamily\bfseries\fontsize{24pt}{28pt}\selectfont You've Reached the Bottom\par}

\vspace{2em}

In a good way.

You've reached the deepest point. You've seen what usually stays in shadow. That takes courage---and you showed it.

\vspace{1.5em}
{\sffamily\bfseries What Now}

What you wrote isn't just answers. It's a map of your inner world. It will change as you change.

\textbf{In a month} reread your notes. You'll be surprised how your perception has shifted.

\textbf{In a year} go through the book again. You'll be a different person---and your answers will be different.

\vspace{1.5em}
{\sffamily\bfseries One Final Question}

What do you now know about yourself that you didn't know before this book?

\vspace{3em}
{\centering\itshape The path continues.\par}

\vspace{3em}
{\centering\sffamily Selfology\par}

\end{document}